Copy number inference with InferCNV

### 2024-05-22 analyses/cell-type-ewings/template_notebooks/04-infercnv.Rmd
match template

```{r}
# get mean value for has_cnv, excluding any NAs
mean_cnv <- cnv_df |> 
  dplyr::filter(!is.na(has_cnv)) |> 
  dplyr::pull(has_cnv) |> 
  mean()

@@

```{r}
# get mean value for mean_proportion, excluding any NAs
all_mean_proportion <- cnv_df |> 
  dplyr::filter(!is.na(mean_proportion)) |> 
  dplyr::pull(mean_proportion) |> 
  mean()

>>>>

```{r}
# get mean value for has_cnv, excluding any NAs
mean_cnv <- mean(cnv_df$has_cnv, na.rm=TRUE)

@@

```{r}
# get mean value for mean_proportion, excluding any NAs
all_mean_proportion <- mean(cnv_df$mean_proportion, na.rm = TRUE)
